upwell_IDX

### 2020-04-21 upwell_IDX.Rmd
update

```{r}
# # Installing and loading libraries
# 
# library(circular)
# ## devtools::install_github("robwschlegel/coastR")
# library(gridExtra)
# library(geosphere)
# library(tidyverse)
# library(heatwaveR)
# library(coastR)
# ```
# 
# # Steps
#   - Use the circular function
#   - Determine daily wind data obtained from 3hr intervals
# 
# ```{r, eval=FALSE}
# wind_1 <- read.delim("Data/Wind_data/wind_data.txt(SAWS)/wind1/wind1.txt", na.strings = "",
#                      col.names = c("station_number", "station_name", "date", "hour", "sub", "speed", "dir"))
# 
# wind_2 <- read.delim("Documents/Data/Wind_data/wind_data.txt(SAWS)/wind2/wind2.txt", na.strings = "",
#                      col.names = c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir"))
# 
# wind_3 <- read.delim("Data/Wind_data/wind_data.txt(SAWS)/wind3/wind3.txt", na.strings = "",
#                      col.names = c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir"))
# 
# # Selecting the important columns for each of the datasets
# ## Renaming the sites within the wind datasets to match the name of the sites at which seawater temperature was collected
# ## The wind data was obtained from the SAWS and the wind stations used were the closes stations to which temperature was collected
# wind_fix <- function(df){
# wind <- df %>%
#   mutate(date = as.Date(as.character(date)),
#          hour = as.numeric(as.character(hour)),
#          dir = as.numeric(as.character(dir)),
#          speed = as.numeric(as.character(speed)),
#          temp_sites = case_when(station_name == "CAPE TOWN TABLE BAY" ~ "Sea Point",
#                                 station_name == "CAPE TOWN - ROYAL YACHT CLUB" ~ "Sea Point",
#                                 station_name  == "PORT NOLLOTH" ~"Port Nolloth",
#                                 station_name  == "CAPE TOWN SLANGKOP" ~ "Hout Bay",
#                                 station_name  == "LAMBERTSBAAI NORTIER" ~ "Lamberts Bay",
#                                 station_name  == "LANGEBAANWEG AWS" ~ "Saldanha Bay")) %>% 
#   dplyr::select(temp_sites, date, hour, dir, speed) %>% 
#   drop_na()
# }
# 
# wind_fix_1 <- wind_fix(df = wind_1)
# wind_fix_2 <- wind_fix(df = wind_2)
# wind_fix_3 <- wind_fix(df = wind_3)
# 
# # Combine and save
# wind_data <- rbind(wind_fix_3, wind_fix_2, wind_fix_1)
# # save(wind_data, file = "Data/wind_data.RData")
# selected_sites <- c("Port Nolloth", "Lamberts Bay", "Sea Point", "Saldanha Bay") #Removed Hout Bay as this is not one of my sites.
# 
# # RWS: Please figure out why some wind direction values are returned as NA
# # RWS: Also, it's not enough to just calculate mean speed. It needs to be taken into account with the directions.
# # RWS: Please look through these resources and make corrections accordingly:
# # https://cran.r-project.org/web/packages/rWind/rWind.pdf
# # https://www.kaggle.com/srlightfoote/example-wind-analysis-in-r
# 
# # Errors in the wind data for Port Nolloth - Recieved the correct wind data with no missing hours
# 
# wind_daily <- wind_data %>%
#   # ungroup() %>%
#   # mutate(date = as.Date(date))%>% # Changing the date to date format
#   filter(temp_sites %in% selected_sites) %>%  # Matching the sites to wind temp sites
#   dplyr::group_by(temp_sites, date) %>%
#   dplyr::summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees", 
#                                                            template = 'geographics')),2)) #, # Direction using the circular function
#                   # mean_speed = round(mean(speed),2)) # Calculating the mean
# save(wind_daily, file = "Data/wind_daily.RData") 
```

@@

# Plotting function
# plot_sites <- function(site_list, buffer, dist){

>>>>

```{r}
# Installing and loading libraries

library(circular)
## devtools::install_github("robwschlegel/coastR")
library(gridExtra)
library(geosphere)
library(tidyverse)
library(heatwaveR)
library(coastR)
```

# Steps
  - Use the circular function
  - Determine daily wind data obtained from 3hr intervals

```{r, eval=FALSE}
wind_1 <- read.delim("Data/Wind_data/wind_data.txt(SAWS)/wind1/wind1.txt", na.strings = "",
                     col.names = c("station_number", "station_name", "date", "hour", "sub", "speed", "dir"))

wind_2 <- read.delim("Data/Wind_data/wind_data.txt(SAWS)/wind2/wind2.txt", na.strings = "",
                     col.names = c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir"))

wind_3 <- read.delim("Data/Wind_data/wind_data.txt(SAWS)/wind3/wind3.txt", na.strings = "",
                     col.names = c("station_number", "station_name", "date", "hour", "sub" ,"speed", "dir"))

# Selecting the important columns for each of the datasets
## Renaming the sites within the wind datasets to match the name of the sites at which seawater temperature was collected
## The wind data was obtained from the SAWS and the wind stations used were the closes stations to which temperature was collected
wind_fix <- function(df){
wind <- df %>%
  mutate(date = as.Date(as.character(date)),
         hour = as.numeric(as.character(hour)),
         dir = as.numeric(as.character(dir)),
         speed = as.numeric(as.character(speed)),
         temp_sites = case_when(station_name == "CAPE TOWN TABLE BAY" ~ "Sea Point",
                                station_name == "CAPE TOWN - ROYAL YACHT CLUB" ~ "Sea Point",
                                station_name  == "PORT NOLLOTH" ~"Port Nolloth",
                                station_name  == "CAPE TOWN SLANGKOP" ~ "Hout Bay",
                                station_name  == "LAMBERTSBAAI NORTIER" ~ "Lamberts Bay",
                                station_name  == "LANGEBAANWEG AWS" ~ "Saldanha Bay")) %>% 
  dplyr::select(temp_sites, date, hour, dir, speed) %>% 
  drop_na()
}

wind_fix_1 <- wind_fix(df = wind_1)
wind_fix_2 <- wind_fix(df = wind_2)
wind_fix_3 <- wind_fix(df = wind_3)

# Combine and save
wind_data <- rbind(wind_fix_3, wind_fix_2, wind_fix_1)
save(wind_data, file = "Data/wind_data.RData")
load("Data/wind_data.RData")
selected_sites <- c("Port Nolloth", "Lamberts Bay", "Sea Point", "Saldanha Bay")

# RWS: Please figure out why some wind direction values are returned as NA
# RWS: Also, it's not enough to just calculate mean speed. It needs to be taken into account with the directions.
# RWS: Please look through these resources and make corrections accordingly:
# https://cran.r-project.org/web/packages/rWind/rWind.pdf
# https://www.kaggle.com/srlightfoote/example-wind-analysis-in-r
wind_daily <- wind_data %>%
  # ungroup() %>%
  # mutate(date = as.Date(date))%>% # Changing the date to date format
  filter(temp_sites %in% selected_sites) %>%  # Matching the sites to wind temp sites
  dplyr::group_by(temp_sites, date) %>%
  dplyr::summarise(dir_circ = round(mean.circular(circular(dir, units = "degrees", 
                                                           template = 'geographics')),2),  # Direction using the circular function
                  mean_speed = round(mean(speed),2)) # Calculating the mean

save(wind_daily, file = "Data/wind_daily.RData") 
```

@@

# Plotting function
plot_sites <- function(site_list, buffer, dist){
